Simulation study in rectangular domain

### 2024-04-17 R/simulation_study/simulation_study_rect.Rmd
changes in simulation_study_rect
fix error in simulation_study_rect + other trials
fix error in simulation_study_rect

```{r global variables}
#number of batch
N_BATCH=2

#number of individual tracks per batch
N_ID=3

@@

n_coeffs=length(sp_coeff_DShore)
coeffs_df=data.frame("estimate"=NA,"coeff_name"=NA)

>>>>

```{r global variables}
#number of batch
N_BATCH=30

#number of individual tracks per batch
N_ID=6

@@

n_coeffs=length(sp_coeff_Dshore)
coeffs_df=data.frame("estimate"=NA,"coeff_name"=NA)
